Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models

### 2020-07-13 analysis/paper/paper.Rmd
changed the title for submitting to Ecosphere, made it appeal to a slightly more general audience. Added an if statement for knitting to Word

title: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"

@@

# when knitting to Word, use this
options(knitr.table.format = "pandoc")

>>>>

title: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"

@@

# when knitting to Word, use this
# what kind of document is being created?
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')

if(doc.type == 'docx') {
  options(knitr.table.format = "pandoc")
}
